Topological Eulerian Synthesis of Slow Motion Periodic Videos

### 2018-02-04 Paper/paper.tex
revised persistence section

\subsection{Persistent Homology}
Our discussion so far has assumed we can find the appropriate $\epsilon$ for the (un)weighted graph Laplacian, but this is data dependent.  The authors of \cite{averbuch2015ringit} use $k$-nearest neighbors, which helps with scale, but which still requires an arbitrary parameter $k$.  To adapt to the data, we 1D leverage persistent homology from topological data analysis \cite{edelsbrunner2010computational}.  Roughly, this framework allows one to find the scale at which topological features exist in point cloud data.  Specifically, we compute the ``1D Vietoris Rips Filtration'' on our sliding window data $X$, which tracks equivalence classes of loops, known as {\em homology classes} \cite{Hatcher}, as edges and triangles are gradually added between sliding window points.  The algorithm returns a ``persistence diagram,'' which is a multiset of points on a 2D birth/death grid, with each point corresponding a loop class.  The birth value $b_i$ indicates the scale $\epsilon$ at which the $i^{\text{th}}$ loop class forms, and the death value $d_i$ indicates the scale at which that class is ``filled in'' (expressible as a formal sum of triangle boundaries with coefficients in some field).  $d_i - b_i$ is known as the {\em persistence} of the $i^{\text{th}}$ class.  For sliding window periodic time series, one point in the diagram should have a much larger persistence than the others (e.g. Figure~\ref{fig:ConceptFigure}) \cite{perea2015sliding,tralie2017quasi}.  We take our scale to be $\frac{1}{2}(b_i + d_i)$ for the largest $d_i - b_i$.  
Finally, note that we compute homology using $\mathbb{Z}_{49}$ coefficients to handle cases where a period has strong harmonics, since, choosing a field which is not relatively prime to a harmonic leads to lowered persistence \cite{perea2015sliding, traliemoebius}.  For instance, a jumping jacks motion has a second harmonic, since an individual jumps twice per cycle, so the common persistence algorithm with $\mathbb{Z}_2$ coefficients would lead to ``M{\"o}bius splitting'' \cite{traliemoebius}.

>>>>

\subsection{Persistent Homology}
Our discussion so far has assumed we can find the appropriate $\epsilon$ for the (un)weighted graph Laplacian, but this is data dependent.
%The authors of \cite{averbuch2015ringit} use $k$-nearest neighbors, which helps with scale, but which still requires an arbitrary parameter $k$.
To adapt to the data, we leverage 1D persistent homology from topological data analysis \cite{edelsbrunner2010computational}.  This framework allows one to find the scale at which topological features exist in point cloud data.  Specifically, we compute the 1D Vietoris Rips Filtration on our sliding window data $X$, which tracks equivalence classes of loops, known as {\em homology classes} \cite{Hatcher}, as edges and triangles are gradually added between sliding window points.  The algorithm returns a so-called persistence diagram, which is a multiset of points on a 2D birth/death grid, with each point corresponding to a loop class.  The birth value $b_i$ indicates the scale at which the $i^{\text{th}}$ loop class forms, and the death value $d_i$ indicates the scale at which that class no longer exists (expressible as a formal sum of triangle boundaries with coefficients in some field).  The difference $d_i - b_i$ is known as the {\em persistence} of the $i^{\text{th}}$ class.  For sliding window periodic time series, one point in the diagram should have a much larger persistence than the others (e.g. Figure~\ref{fig:ConceptFigure})~\cite{perea2015sliding,tralie2017quasi}, and this ideally reflects the single cycle of motion that we seek.  We take our scale to be $\frac{1}{2}(b_i + d_i)$ for the largest $d_i - b_i$. % MSB: last sentence might change based on experiments

Finally, homology computation requires the specification of coefficients that belong to a user-given field. Coefficients in $\mathbb{Z}_2$ are commonly chosen, however in our scenario this is problematic. For instance, the motion of someone performing a jumping jack contains a second harmonic, since an individual jumps twice per cycle, and using coefficients in $\mathbb{Z}_2$ would lead to so-called M{\"o}bius splitting~\cite{traliemoebius}. Thus, we use coefficients in the field $\mathbb{Z}_{49}$ in order to capture these types of complex motions.
% MSB: mention use of software in experiments, not in techniques

%Finally, note that we compute homology using $\mathbb{Z}_{49}$ coefficients to handle cases where a period has strong harmonics, since, choosing a field which is not relatively prime to a harmonic leads to lowered persistence \cite{perea2015sliding, traliemoebius}.  For instance, a jumping jacks motion has a second harmonic, since an individual jumps twice per cycle, so the common persistence algorithm with $\mathbb{Z}_2$ coefficients would lead to ``M{\"o}bius splitting'' \cite{traliemoebius}.  We use the GUDHI library\cite{maria2014gudhi} to compute persistent homology quickly with fields other than $\mathbb{Z}_2$.
